Thoughts about cognition

### 2015-11-05 cogniveProcessing/summery.tex
added more texts :*(

>>>>

\subsection{Processing vision}
\subsubsection{Horizontal cells}
It processes it with cirlces and there is some basic logic
going on when the signals leave the eyes (nand gates and such).

\subsubsection{V1}
Processes light and dark paterns, the cells aren't to pickey (always give
of some signal) but some have preference for certain orientations.

\subsubsection{V2}
% A heuristic layer?
Responds to known rules of the visual world. Patterns we are used to seeing.

Receptive fields go from simple and small to progresivley complex and large.

\subsubsection{After V2}
Things become very complex very fast.

\subsection{Scanning techniques}

\subsubsection{MRI}
Magnatic resonanse imaging, fMRI is the same but uses
the diff of 2 images. MRI always uses blood oxygion
levels to get an image.

\paragraph{DPRI}
Same as MRI but measures water instead of oxygian.
This can potantioally image communcation between parts
of the brain. But its a work in progress.

\subsection{EEG}
Measure the activity in the brain, great temporal res,
but bad spatial res.

\paragraph{ECoG}
EEG with open skull. Great temporal and good spatial res.
But its invasive, so there is little opertunity to o this.

\subsubsection{MEG}
Best thing, has high temporal and spatial resolution.
But is very expensive.

\subsubsection{TMS}
The zapping. It does not give an image but it interferes
with brain activity instead by sending and EMP.
% I'm going to stay away from this one.

\paragraph{rTMS} Long term TMS by using repeated zaps.
It may work as an antidrepresant, but drug companys try to fight these 
results.

\subsubsection{Drugs}

You can also use drugs to mess with the brain.
